```{r message=TRUE}
library(glmmTMB)
library(tidyverse)
edv <- read.csv("C:/Users/baois/Desktop/URES/ed_data.csv")
hi <- read.csv("C:/Users/baois/Desktop/URES/uresw5/region_daily_weighted_heat_index.csv")
str(edv)
str(hi)

edv <- edv %>%
  mutate(Region = as.integer(str_remove(geo, "Region")),
         Date = as.Date(as.character(temporal), format = "%Y%m%d")) %>%
  select(Region, Date, dataValue) %>%
  rename(ed_visits = dataValue)
hi <- hi %>%
  rename(Region = HHS.Region, heat_index = Region_Weighted_Heat_Index) %>%
  mutate(Date = as.Date(Date)) 

merged <- edv %>%
  right_join(hi)
str(merged)
```

Testing random effect of seasonality

```{r}
merged <- merged %>%
  mutate(
    day_of_year = yday(Date),
    sin_doy = sin(2 * pi * day_of_year / 365),
    cos_doy = cos(2 * pi * day_of_year / 365)
  )
#fix seasonal 
model_fixed <- glmmTMB(
  ed_visits ~ sin_doy + cos_doy,
  family = nbinom2(link = "log"),
  data = merged
)
#mix seasonal
model_random <- glmmTMB(
  ed_visits ~ sin_doy + cos_doy + (1 + sin_doy + cos_doy | Region),
  family = nbinom2(link = "log"), #convergence warning, but can still run
  data = merged
)

anova(model_fixed, model_random)

```

p \< 0.05, random effect is significant

Testing random effect of heat index

```{r}
merged <- merged %>%
  arrange(Region, Date) %>%
  group_by(Region) %>%
  mutate(lag10_heat = lag(heat_index, n = 10)) %>%
  ungroup()
#mix seasonal + fix heat
model_fixed_heat <- glmmTMB(
  ed_visits ~ sin_doy + cos_doy + lag10_heat + (1 + sin_doy + cos_doy | Region),
  family = nbinom2(link = "log"),
  data = merged
)
#mix seasonal + mix heat 
model_random_heat <- glmmTMB(
  ed_visits ~ sin_doy + cos_doy + lag10_heat + (1 + sin_doy + cos_doy + lag10_heat | Region),
  family = nbinom2(link = "log"),
  data = merged
)

anova(model_fixed_heat, model_random_heat)
summary(model_fixed_heat)
str(merged)
```

We are still missing fix heat only, random heat only and fix seasonal + fix heat models

We'll add them and compare all together

```{r}
model_random_intercept <- glmmTMB(
  ed_visits ~ sin_doy + cos_doy + (1| Region),
  family = nbinom2(link = "log"),
  data = merged
)

model_only_heat_fixed <- glmmTMB(
  ed_visits ~ lag10_heat,
  family = nbinom2(link = "log"),
  data = merged
)

model_only_heat_random <- glmmTMB(
  ed_visits ~ lag10_heat + (1 + lag10_heat | Region),
  family = nbinom2(link = "log"),
  data = merged
)

model_fixed_season_fixed_heat <- glmmTMB(
  ed_visits ~ sin_doy + cos_doy + lag10_heat,
  family = nbinom2(link = "log"),
  data = merged
)

aic_results <- AIC(
  model_only_heat_fixed, 
  model_only_heat_random, 
  model_fixed, 
  model_random,
  model_fixed_season_fixed_heat, 
  model_fixed_heat, 
  model_random_heat,     
  model_random_intercept
)

aic_df <- as.data.frame(aic_results)
aic_df %>%
  arrange(AIC)
```

select glmmtmb family

add a random intercept ie. (1 \| Region)

lag selection and pre whitening one of edv and hi(read Time Series Analysis and Its Applications example 5.8)
